    \documentclass[12pt]{letter}
    \textwidth=6.25in
    \textheight=8.75in
    \footskip=1in
    \oddsidemargin=0in
    \topmargin=-1.0in
    \usepackage{amssymb}
    \usepackage{amsmath}
	\usepackage{cmbright}
	\usepackage{color}

    \include{NAMacros}
	
    \begin{document}
    \begin{center}
{\LARGE\sc Homework 01, Math 515 \\ 15 February, 2024}
	\end{center}
	
	\bigskip

{\Large\bf\sc Name:}
	\\
    \bigskip
    \line(1,0){200}
    \\
	\begin{enumerate}
	
	\item
Suppose that $f(\varepsilon) = 1-\cos^2(\varepsilon)$, for $\varepsilon >0$. 
	\begin{enumerate}
	\item
Show that
	\[
f(\varepsilon) = O(\varepsilon^2), \quad \mbox{as}\quad\varepsilon\searrow 0.	
	\]
	\item
Show that
	\[
f(\varepsilon) = o(\varepsilon), \quad \mbox{as}\quad\varepsilon\searrow 0.	
	\]
	\end{enumerate}
	
	\item
Show that
	\[
\log(1+\varepsilon) = O(\varepsilon)	, \quad \mbox{as}\quad\varepsilon\searrow 0.
	\]

	\item
Consider the problem
	\[
y'(t) + y(t) = \varepsilon y^2(t), \quad y(0) = 1,	
	\]
for $t\ge 0$, and $\varepsilon >0$.
	\begin{enumerate}
	\item
Determine a three-term expansion for small $\varepsilon>0$ using the perturbation approach. Assume the standard asymptotic power series approximation is valid, as $\varepsilon\searrow 0$.

	\item
Show that the exact solution is
	\[
y(t) = e^{-t}\left[ 1+ \varepsilon(e^{-t}-1)\right]^{-1}.	
	\]
	
	\item
Expand the exact solution for small $\varepsilon$ and compare with the result from part (a).

	\item
Are the expansions you obtained valid for all $t\ge 0$?

	\end{enumerate}
	
	\item
Consider the solution of the equation
	\[
y'(x) + y(x) = \frac{1}{x},	
	\]
for $x>0$. In seeking an approximation for large $x$, assume that 
	\[
y(x) \sim \sum_{k=1}^\infty  \frac{a_k}{x^k}, \quad \mbox{as} \quad  x\nearrow\infty.	
	\]
	\begin{enumerate}
	\item
Substitute this expansion into the equation to determine the coefficients. 

	\item
Does the series you have produced converge? 
	\end{enumerate}
	
	\item
Consider the van der Pol oscillator problem:
	\[
u''(t) +u(t) = \varepsilon(1-u^2(t)) u'(t),	
	\]
for $t\ge 0$ and $\varepsilon >0$. Suppose that
	\[
u(t,\varepsilon) \sim \sum_{k=0}^\infty u_k(t)\varepsilon^k , \quad \mbox{as} \quad \varepsilon\searrow 0.	
	\]
	\begin{enumerate}
	\item
Substitute this expansion in the differential equation and find $u_0$ and $u_1$ for general initial data.

	\item
Plot your two-term composite approximate solution for a couple of interesting initial data choices.
	\end{enumerate}
	
	\item
Determine the second-order (three term) asymptotic expansion for the solution of 
	\[
u''(t) + u(t) = \varepsilon u^2(t),
	\]
for $t\ge 0$, with $u(0) = a$ and $u'(0) = 0$, as $\varepsilon \searrow 0$. Is this expansion uniformly valid for $t\ge 0$? If not, can you restrict the domain of the solution/approximation so that it is? 
	
	
	\item
Find an asymptotic series expansion for the integral
	\[
I(\lambda) = \lambda\int_0^\infty \frac{e^{-t}}{\lambda + t} \, \mathrm{d} t,	
	\]
as $\lambda\nearrow \infty$.

	\item
Suppose that 
	\[
f(\lambda) \sim \sum_{k =0}^\infty \frac{a_k}{\lambda^k}, \quad \mbox{as} \quad \lambda \nearrow \infty.	
	\]
	\begin{enumerate}
	\item
Find the first few terms in the asymptotic expansion, as $\lambda\to\infty$ of $\frac{1}{f(\lambda)}$.
	\item
Find the first few terms in the asymptotic expansion, as $\lambda\to\infty$ of $p(f(\lambda))$, where $p$ is a polynomial.
	\end{enumerate}
	
	\end{enumerate}
	
    \end{document}